---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# engate

<!-- badges: start -->
[![R-CMD-check](https://github.com/BernardoCGdaSilva/engate/workflows/R-CMD-check/badge.svg)](https://github.com/BernardoCGdaSilva/engate/actions)
<!-- badges: end -->

engate is a package which aims to help data manipulation of brazilian public data. It consists of two sets of functions - nomeia and traduz - the former matchs an index column with its description and the latter, a related index.

## Installation

You can install the development version of engate from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("BernardoCGdaSilva/engate")
```

## Examples

This is an example of the nomeia set of functions:

```{r example 1}
library(engate)
df1 <- data.frame(codigos_cbo = c("010105", "515220", "992115"))
df2 <- nomeia_cbo(df1,"codigos_cbo")
df2
```

And this is an example of the traduz set:

```{r example 2}
library(engate)
df1 <- data.frame(codigos_ncm = c("01012100", "35052000", "84459030"))
df2 <- traduz_ncm_cnae(df1, "codigos_ncm")
df2
```
